---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(plastyr)
```

## Country Proportion Plastic Type Summary Statistics

```{r}
#| eval: false
country_plastic_prop(plastic_data, country = "United States")
```

Will return the proportion of user specified (or default United States) country's 
total plastic for each type.

## Top n Countries Total Plastic Plot

```{r}
#| eval: false
plot_plastic_by_country(plastic_data, top_n = 10)
```

Creates a bar chart of the top n (specified by user input default 10) countries,
in descending order. The y axis representing total plastic pollution, x axis representing
the countries.

## Top n Polluters of Plastic Type

```{r}
#| eval: false
top_polluters(plastic_data, n = 5, plastic_type = "pet")
```

Returns a data frame of the top n (default 5) countries polluting the user 
specified plastic type (default "PET") in descending order. One column for the country
and one for the count of the user specified plastic type.


