---
title: "Introduction to plastyr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to plastyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load Data

First, load the dataset bundled with the package:

```{r}
library(plastyr)
plastic <- load_data()
```

## Clean Data

Remove invalid rows and standardize country names:

```{r}
clean <- clean_plastics(plastic)
```

## Country Plastic Type Proportions

Get the proportion of each plastic type for a specific country:

```{r}
country_plastic_prop(plastic, country_name = "China")
```

## Top Polluting Countries

Return the top N countries by total plastic collected:

```{r}
top_polluters(plastic, n = 5)
```

## Plot Plastic by Country

Bar chart of the top N countries by total plastic:

```{r}
plot_plastic_by_country(plastic, top_n = 10)
```

## Plot Top Polluters

Alternative bar chart visualization of top polluters:

```{r}
plot_top_polluters(plastic, n = 10)
```

## Linear Model of Plastic Over Time

Fit a simple linear regression of total plastic collected vs. year 
for a given country:

```{r}
plastic_lm(plastic, country_name = "China")
```


